A load balancing scheme for massively multiplayer online games \thanks{This work was supported by the National Research Council (CNPq) and by the Coordination of Improvement of Higher Education (CAPES), both brazilian research funding agencies.}

### 2009-04-10 textos/dissertation/MTAP_LaTeX/pub/tex/latex/svjour3/global/balancing.tex

In the case when $U_{total} \leq 1$, there is sufficient power in the system so that all servers have a usage smaller than 100\%. Thus, regions are added to the group until all the servers involved are using fewer resources than they have. However, when $U_{total} > 1$, there is no way to all servers be using less than 100\% of its resources at the same time. Thus, it is sufficient that all servers are similarly overburdened, and that some kind of adjustment is made, which will probably be a reduction in the information sent to players in each state update.

@@

>>>>

In the case when $U_{total} \leq 1$, there is sufficient power in the system so that all servers have a usage smaller than 100\%. Thus, regions are added to the group until all the servers involved are using fewer resources than they have. However, when $U_{total} > 1$, there is no way to all servers be using less than 100\% of its resources at the same time. Thus, it is sufficient that all servers are similarly overburdened, and that some kind of adjustment is made, which will probably be a reduction in the information sent to players in each state update. Although this approach seems to lead the system to an inconsistent state, due to the lack of available bandwidth, the $U_{total}$ is calculated based on the theoretical value of a region's weight. In practice, the system as a whole will take two measures: first, the frequency at which state updates are sent to players is diminished and, second, it will deny access to new players who try to join the game. Denying access when the game is overpopulated with players is the usual policy adopted by some MMOGs.

@@

It is important to notice that the while condition (line \ref{alg:ggp:whilefraction}) may lead to the assignment of a cell whose weight is higher than the weight share left on the region. However, it is very unlikely to assign to a region its exact weight share, so it is preferrable to surpass this value, guarateeing that every cell will be assigned to some region. Also, assigning to a region a weight which is higher than its calculated share does not imply that it will become overloaded. First, the weight share of a region is not equal to the power of its server. When there are enough resources, the region's weight share will be smaller than its capacity. Furthermore, as \ggp\ is a greedy algorithm, the heaviest cells will be assigned first, to the most powerful servers.
